---
title: "US Wildfire Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)

bar_chart <- function(label, width = "100%", height = "14px", fill = "#00bfc4", background = NULL) {
  bar <- htmltools::div(style = list(background = fill, width = width, height = height))
  chart <- htmltools::div(style = list(flexGrow = 1, marginLeft = "6px", background = background), bar)
  htmltools::div(style = list(display = "flex", alignItems = "center"), label, chart)
}

`%>%` <- magrittr::`%>%`
load("./data/us_wildfire_map.RData")
load("./data/us_wildfire_poly.RData")

df <- poly %>% dplyr::select(object_id = OBJECTID, incident_name = IncidentName,
                             IMT_name = IMTName, unit_id = UnitID,
                             map_method = MapMethod, comments = Comments,
                             gis_acres = GISAcres, shape_area = Shape__Area, global_id_2 = GlobalID_2) %>%
  dplyr::distinct()
```

Map
===================================== 

```{r map}
m
```

Data
===================================== 
```{r table}


table <- reactable::reactable(data = df, 
                              pagination = FALSE,
                              highlight = TRUE,
                              height = 1200,
                              defaultSorted = "gis_acres",
                              sortable = TRUE,
                              borderless = TRUE,
                              defaultPageSize = nrow(df),
                              columns = list(
                                object_id = reactable::colDef(name = "Object ID"),
                                incident_name = reactable::colDef(name = "Incident Name"),
                                IMT_name = reactable::colDef(name = "IMT Name"),
                                unit_id = reactable::colDef(name = "Unit ID"),
                                map_method = reactable::colDef(name = "Map Method"),
                                comments = reactable::colDef(name = "Comments"),
                                gis_acres = reactable::colDef(name = "GIS Acres",
                                                              sortable = TRUE,
                                                              defaultSortOrder = "desc",
                                                              # format = reactable::colFormat(separators = TRUE, digits = 0),
                                                              cell = function(value) {
                                                                width <- paste0(value * 100 / max(df$gis_acres), "%")
                                                                # Add thousands separators
                                                                value <- format(value, big.mark = ",")
                                                                bar_chart(value, width = width, fill = "red")
                                                              },
                                                              align = "left"),
                                shape_area = reactable::colDef(name = "Shape Area",
                                                               format = reactable::colFormat(separators = TRUE, digits = 5)),
                                global_id_2 = reactable::colDef(name = "Global ID")
                                
                              ))


htmltools::div(class = "us-wildfire",
               htmltools::div(class = "us-wildfire-header",
                              htmltools::div(class = "us-wildfires-title", "Source: National Interagency Fire Center ArcGIS Online Site"),
                              
                              paste("Last Update: ", run_time, " PST", sep = "")
               ),
               table
)

```

About
===================================== 


**The US Wildfire Dashboard**

The US Wildfire Dashboard provides an overview of the ongoing wildfire in the US. This dashboard is built with R using [Rmakrdown](https://rmarkdown.rstudio.com/) and [flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/) framework, and can easily reproduce by others. The code behind the dashboard available [here](https://github.com/RamiKrispin/uswildfire)

**Data**

The input data for this dashboard is the [National Interagency Fire Center ArcGIS Online Site](https://data-nifc.opendata.arcgis.com/).

Data on the dashboard is refreshed hourly with [Github Actions](https://github.com/RamiKrispin/uswildfire/blob/master/.github/workflows/data_refresh.yml), where the raw data on the NIFC website is getting updated every few hours.


**Packages**

* Dashboard interface - the [flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/) package. 
* Mapping - [leaflet](https://rstudio.github.io/leaflet/) for plotting the map and [sf](https://r-spatial.github.io/sf/index.html) packages
* Data - [jsonlite](https://github.com/jeroen/jsonlite) for parsing the raw data
* Tables - the [reactable](https://glin.github.io/reactable/) package

**Deployment and reproducibly**

The dashboard was deployed to Github docs. If you wish to deploy and/or modify the dashboard on your Github account, you can apply the following steps:

* Fork the dashboard [repository](https://github.com/RamiKrispin/uswildfire), or
* Clone it and push it to your Github package
* Here some general guidance about deployment of flexdashboard on Github page - [link](https://github.com/pbatey/flexdashboard-example)


**Docker**

The supporting docker with the requirement packages for running this dashboard is available [here](https://hub.docker.com/repository/docker/rkrispin/us_wildfire). To run the dashboard localy with RStudio follow the following steps:

* Clone the the dashboard [repository](https://github.com/RamiKrispin/uswildfire)
* Run the following docker:

``` bash
docker run -p 8787:8787 -e PASSWORD='Your_Password' -e USER='Your_Username' -v ~/your_local_path  rkrispin/us_wildfire_rstudio:dev
```

Where the `Your Password` and `Your Username` above should replace with the password and username you wish to set for the RStudio instance. The `your_local_path` argument should replace with the local path of the cloned dashboard on your machine. Once the docker is lunched, use on your browser `http://localhost:8787` for login RStudio (using the credential you set above) and access the dashboard on sub-folder `uswildfire` and render the `index.Rmd` file to lunch the dashboard.



For any question or feedback, you can either open an [issue](https://github.com/RamiKrispin/uswildfire/issues) or contact me on [Twitter](https://twitter.com/Rami_Krispin).

